\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2018-04-04 redaction/dhp_july2017.tex
Figure 1 more

\begin{figure}[htbp]
\caption{Trend in Transport costs (Yearly mean value, 3 digits, in \% of the fas price)}
\label{fig:decomp_TC_3d}
\begin{center}
\begin{tabular}{cc}
{\small (a) Air } & {\small (b) Vessel}\\
\includegraphics[width=3in, height=2.5in]{Fig2a_decompTC_air_3d.pdf}
& \includegraphics[width=3in,height=2.5in]{Fig2b_decompTC_vessel_3d.pdf} \\
\end{tabular}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Trend in Transport costs (Yearly mean value, 3 digits, in \% of the fas price, 1989 exclude for "Air")}
\label{fig:decomp_TC_3d}
\begin{center}
\includegraphics[width=6.5in, height=5in]{Figure1_Trend_of_total_TC_by_mode.pdf}
\end{center}
\end{figure}
